\documentclass[a4paper,12pt]{article}

% Packages
\usepackage[utf8]{inputenc} % Encoding
\usepackage[T1]{fontenc}  % Font encoding
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}     % Hyperlinks
\usepackage{geometry}     % Page layout
\usepackage{listings}     % Code listings
\usepackage{xcolor}       % Colors for code

% Page layout
\geometry{margin=1in}

% Code formatting
\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    keywordstyle=\color{blue},
    commentstyle=\color{green!70!black},
    stringstyle=\color{red},
    showstringspaces=false,
    numbers=left,
    numberstyle=\tiny\color{gray},
    stepnumber=1,
    numbersep=5pt,
}

% Metadata
\title{Developer Guide for Project \texttt{HDF5\_BLS}}
\author{Pierre Bouvet}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\section{Introduction}
This document serves as the developer guide for the \texttt{HDF5\_BLS} project. It provides details about the project structure, coding conventions, and instructions for development and contribution.

\section{Project Structure}
The project has the following structure:
\begin{verbatim}
HDF5_BLS/
|-- .github/
|-- docs/
|-- guides/
|-- HDF5_BLS/
|-- HDF5_BLS_GUI/
|-- spreadsheets/
|-- tests/
|-- .gitignore
|-- CONTRIBUTING.md
|-- LICENSE.md
|-- pyproject.toml
|-- README.md
|-- requirements.txt
|-- setup.py
\end{verbatim}

\subsection{Key Components}
\begin{itemize}
    \item \textbf{.github/}: GitHub configuration files.
    \item \textbf{docs/}: Documentation files for the project.
    \item \textbf{guides/}: The repository to find guides and extra documentation.
    \item \textbf{HDF5\_BLS/}: Contains the source code for the project.
    \item \textbf{HDF5\_BLS\_GUI/}: Contains the source code for the GUI.
    \item \textbf{spreadsheets/}: Contains example and reference spreadsheets for the parameters of the instrument and measures.
    \item \textbf{tests/}: Contains unit tests for the project.
    \item \textbf{.gitignore}: Specifies files and directories to be ignored by Git.
    \item \textbf{CONTRIBUTING.md}: Guidelines for contributing to the project.
    \item \textbf{LICENSE.md}: License for the project.
    \item \textbf{pyproject.toml}: Configuration file for the Python project.
    \item \textbf{README.md}: Overview of the project.
    \item \textbf{requirements.txt}: Specifies the Python dependencies.
    \item \textbf{setup.py}: Defines the package and installation requirements.
\end{itemize}

\section{Installation}
To set up the project locally:
\begin{enumerate}
    \item Clone the repository:
    \begin{lstlisting}[language=bash]
    git clone https://github.com/PierreBouvet/HDF5_BLS_v1
    cd HDF5_BLS_v1
    \end{lstlisting}
    \item Install the required dependencies:
    \begin{lstlisting}[language=bash]
    pip install -r requirements.txt
    \end{lstlisting}
\end{enumerate}

\section{Running the Tests}
To ensure the code is working as expected, run the tests using the following command:
\begin{lstlisting}[language=bash]
pytest
\end{lstlisting}

\section{Development Workflow}
\subsection{Branching Strategy}
Use the following Git branching strategy:
\begin{itemize}
    \item \textbf{main}: Stable code ready for production.
    \item \textbf{feature/\{name\}}: New features under development.
    \item \textbf{bugfix/\{name\}}: Bug fixes.
\end{itemize}

\section{Contribution Guidelines}
\begin{itemize}
    \item Fork the repository and create a new branch for your changes.
    \item Ensure all tests pass before submitting a pull request.
    \item Write clear and concise commit messages.
    \item Provide detailed descriptions in pull requests.
    \item Add tests for new features or bug fixes in the \texttt{tests/} directory.
\end{itemize}

\section{Contact}
For questions or suggestions, please contact the maintainer at \href{mailto:pierre.bouvet@meduniwien.ac.at}{pierre.bouvet@meduniwien.ac.at}.

\end{document}
