To install the package, you can either download the source code from the GitHub repository or use pip to install the package. We recommend using pip for users who do not intend on working on the package as it is the easiest way to install the package.

\paragraph{Using pip}
    To install the package using pip, run the following command:
\begin{lstlisting}
pip install HDF5_BLS
\end{lstlisting}   

\paragraph{Downloading the source code}
The source code can be downloaded from the GitHub repository: \url{https://github.com/bio-brillouin/HDF5_BLS}. To download the source code, click on the green button "Code" and then click on the "Download ZIP" button. Once the download is complete, unzip the file and open a terminal in the folder where the code is stored. To install the package, run the following command:
\begin{lstlisting}
pip install .
\end{lstlisting}

This will install the package and all its dependencies. To check if the package was installed correctly, run the following command:
\begin{lstlisting}
python -c "import HDF5_BLS"
\end{lstlisting}

If the package was installed correctly, the command will not return any error.

\paragraph{The Wrapper object}

The \texttt{Wrapper} object is the main class of the package. Its role is to interface the HDF5 file and the code while ensuring a safe access to the data and a conservation of the structure of the file. This class is meant to do these four actions:
\begin{itemize}
    \item Create a structure that is universal to the BioBrillouin community in a seamless manner.
    \item Allow the user to acces the data and attributes of the file.
    \item Allow the user to add data to the file with attributes that are specific to the BioBrillouin community.
    \item Allow the user to add or modify attributes of the file.
\end{itemize}

To use this object, the user must first import it from the HDF5\_BLS package:
\begin{lstlisting}
from HDF5_BLS.wrapper import Wrapper
\end{lstlisting}


 