\documentclass{book}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{amsmath}

\title{Interactive UI Tutorial}
\author{Your Name}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\chapter{Introduction}
Welcome to the interactive UI tutorial. This book will guide you through the steps to create and use the UI effectively.

\chapter{Getting Started}
\section{Installation}
To get started, you need to install the necessary software. Follow the instructions below:

\begin{itemize}
    \item Step 1: Download the software from \href{http://example.com}{this link}.
    \item Step 2: Run the installer and follow the on-screen instructions.
    \item Step 3: Verify the installation by running the following command:
\end{itemize}

\begin{lstlisting}[language=bash]
$ verify-installation
\end{lstlisting}

\section{First Steps}
Once the installation is complete, open the software and follow these steps:

\begin{enumerate}
    \item Open the application.
    \item Create a new project by clicking on \textbf{File} $\rightarrow$ \textbf{New Project}.
    \item Enter the project details and click \textbf{Create}.
\end{enumerate}

\chapter{Using the UI}
\section{Main Interface}
The main interface consists of several sections:

\begin{itemize}
    \item \textbf{Toolbar}: Contains shortcuts to frequently used actions.
    \item \textbf{Sidebar}: Provides access to different modules.
    \item \textbf{Main Area}: Displays the content you are working on.
\end{itemize}

\section{Toolbar}
The toolbar allows you to quickly access common actions. Here are some of the main buttons:

\begin{itemize}
    \item \textbf{Save}: Saves the current project.
    \item \textbf{Open}: Opens an existing project.
    \item \textbf{Settings}: Opens the settings menu.
\end{itemize}

\chapter{Advanced Features}
\section{Customization}
You can customize the UI to suit your preferences. To do this, go to \textbf{Settings} $\rightarrow$ \textbf{Customize UI}.

\section{Shortcuts}
Here are some useful keyboard shortcuts:

\begin{itemize}
    \item \textbf{Ctrl+S}: Save the current project.
    \item \textbf{Ctrl+O}: Open an existing project.
    \item \textbf{Ctrl+P}: Print the current document.
\end{itemize}

\chapter{Troubleshooting}
\section{Common Issues}
If you encounter any issues, refer to the following solutions:

\begin{itemize}
    \item \textbf{Issue 1}: The application won't start.
    \begin{itemize}
        \item Solution: Check if all dependencies are installed.
    \end{itemize}
    \item \textbf{Issue 2}: Unable to save the project.
    \begin{itemize}
        \item Solution: Ensure you have write permissions to the project directory.
    \end{itemize}
\end{itemize}

\end{document}